Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-13 article.tex
Better explained how photothrombosis and pO2 measurements could be performed simultaneously

\subsection{Oxygen Tension and Blood Flow during Photothrombosis}
Targeted photothrombosis within a descending arteriole can be seen in the series of speckle contrast images in Fig.~\ref{fig:photothrombosis}a. The red overlay in the first frame depicts the 0.09 mm$^{2}$ region illuminated with DMD-targeted 532 nm light for 420 seconds. The remaining frames depict the progression of the photothrombotic occlusion as the targeted vessel undergoes stenosis and flow is significantly reduced. After two minutes of exposure, the occluded area is indistinguishable from the surrounding parenchyma.

Fig.~\ref{fig:photothrombosis}b depicts the five regions targeted for continuous relative blood flow and \pO\ measurements. The first arteriole region (A1) is the same vessel targeted for photothrombotic occlusion. The resulting timecourses of relative blood flow and \pO\ within each region can be seen in Fig.~\ref{fig:photothrombosis}c. By $t = 120$ s, relative flow within the targeted arteriole decreased to \textless50\% of baseline and \pO\ fell from 80 mmHg to only 20 mmHg. The propagation of an ischemia-induced depolarization event \cite{Shin:2006dc,Dreier:2011gz} can be seen beginning at $t = 300$ s with sharp reductions in both relative flow and \pO. As the depolarization subsided, flow within the targeted arteriole further decreased to \textless35\% of baseline while the \pO\ returned to pre-depolarization levels around 20 mmHg.

>>>>

\subsection{Oxygen Tension and Blood Flow during Photothrombosis}
Targeted photothrombosis within a descending arteriole can be seen in the series of speckle contrast images in Fig.~\ref{fig:photothrombosis}a. The red overlay in the first frame depicts the 0.09 mm$^{2}$ region illuminated with DMD-targeted 532 nm light for 420 seconds. Because Oxyphor PtG4 has minimal absorbance of green light (Fig.~\ref{fig:oxyphor_ptg4}a), \pO\ measurements using 445 nm excitation were simultaneously acquired from the same region. The remaining frames depict the progression of the photothrombotic occlusion as the targeted vessel undergoes stenosis and flow is significantly reduced. After two minutes of exposure, the occluded area is indistinguishable from the surrounding parenchyma.

Fig.~\ref{fig:photothrombosis}b depicts the five regions targeted for continuous relative blood flow and 445 nm \pO\ measurements. The first arteriole region (A1) is the same vessel targeted for photothrombotic occlusion. The resulting timecourses of relative blood flow and \pO\ within each region can be seen in Fig.~\ref{fig:photothrombosis}c. By $t = 120$ s, relative flow within the targeted arteriole decreased to \textless50\% of baseline and \pO\ fell from 80 mmHg to only 20 mmHg. The propagation of an ischemia-induced depolarization event \cite{Shin:2006dc,Dreier:2011gz} can be seen beginning at $t = 300$ s with sharp reductions in both relative flow and \pO. As the depolarization subsided, flow within the targeted arteriole further decreased to \textless35\% of baseline while the \pO\ returned to pre-depolarization levels around 20 mmHg.
